Lattice Boltzmann simulations of magnetically responsive\\ ellipsoidal particle stabilized emulsions

### 2025-03-20 chapters/paper3.tex
Fixed some first person wording in aim 3

From Figure \ref{fig:stress_strain}, the slopes of the curve indicate a non-linear shear response to the applied strain rate, suggesting that the rheological properties
are non-Newtonian. Bijels stabilized by prolate and oblate particles also have different shear properties. For bijels stabilized by oblate particles, the stress curves
are more spread out suggesting that there is a larger variance in the properties arising from the change in the initial microstructure of the bijel. From the plot
we can see that the increase in particle order reduces the yield stress of the bijel. For bijels stabilized by rod like particles, the stress response of each processing 
condition is closer together, indicating a smaller variation in the response to the applied magnetic field compared to oblate particles. The shear response upon application
of the magnetic field also suggest that increased ordering of prolate particles makes the bijel more resistant to shear. I quantify the Herschel-Buckley fit parameters and 
tabulate the results in Table \ref{table:rheology_fit}.

@@

In Figure \ref{fig:particle_viz_tz}, the particles are initially ordered to the direction of the applied magnetic field. Upon application of shear and removal
of the magnetic field, I see that the particles begin reorienting away from the z direction. I also observe that the reorientation of particles uncovers the interface.
The reorientation observed is particle morphology specific with prolate particles seeing more reorientation away from the applied shear direction than oblate particles.
Looking at the images, I see that prolate particles rotate away from the direction of the magnetic field and applied shear towards the direction of the shear gradient,
while oblate particles reorient towards minimizing area to the applied shear direction. While these snapshots show the initial and final orientations of the particles at the
interface, we can characterize the time evolution of the particle monolayer changes to identify its role in the rheological properties characterized.

@@

From Figure \ref{fig:interface_angle_shear}, I demonstrate that there is a slow increase in the interface angle over time for all cases
except for $\bar{B}: 0 \to 1$. For the $\bar{B}: 0 \to 1$ case, this has been shown in Chapter \ref{chapter:aim2} to be due to particle
reorientation to the applied magnetic field. For all other cases, we see an average increase in $\langle \psi \rangle$ over time, showing
that the particles under shear reorient out of the interface. Particles reorienting out of the interface can be due to shear induced interfacial 
stress, modifying the curvature of the interface and thus the lowest energy particle orientation to the interface or shear induced increases in
interparticle forces, causing the particle to tilt out of the interface to minimize interparticle forces. We can characterize the latter 
mechanism through measurements of the number of particles on the interface as increases in interparticle forces result in ejection of
particles from the interface.

@@

From the results in Figure \ref{fig:particles_interface_prop_shear}, the impact of the initial microstructure on the number of particles on the interface
differs for bijels stabilized by oblate and prolate ellipsoids. We split this analysis on processing history. While keeping the applied magnetic field
the same, we see little differences in the behavior of $n_{int}$, with their behavior corresponding to changes in $\langle \psi \rangle$. 
Looking at the case of $\bar{B}:0 \rightarrow 0$, there is little change in the number of particles at the interface upon application of shear. This implies that the 
particles remain strongly adsorbed on the
interface. The $\langle \psi \rangle$ results also show this as we see this parameter increasing slowly. This suggests that the particles remain firmly adsorbed
on the interface. Looking to the $\bar{B}:0 \rightarrow 1$ case, the number of particles at the interface drops while $\langle \psi \rangle$ increases. This
trend affects both particles which suggests that shear can pull particles out of the interface due to the decreased
interfacial adsorption energy the particle experiences when rotating out of the interface to orient to the applied field. The $\bar{B}:1 \rightarrow 1$ and 
$\bar{B}:1 \rightarrow 0$ have strong dependences on particle morphology. While an increase in $\langle \psi \rangle$ can be seen in both processing histories 
for both particle morphologies, a decrease in $n_{int}$ can be seen for prolate particles with processing history $\bar{B}:1 \rightarrow 0$ and for 
oblate particles with processing history $\bar{B}:1 \rightarrow 1$. We visualize $\langle \psi \rangle$ at the initial and final timestep for bijels stabilized with
oblate and prolate particles with processing $\bar{B}:1 \rightarrow 0$.

>>>>

From Figure \ref{fig:stress_strain}, the slopes of the curve indicate a non-linear shear response to the applied strain rate, suggesting that the rheological properties
are non-Newtonian. Bijels stabilized by prolate and oblate particles also have different shear properties. For bijels stabilized by oblate particles, the stress curves
are more spread out suggesting that there is a larger variance in the properties arising from the change in the initial microstructure of the bijel. From the plot
the increase in particle order reduces the yield stress of the bijel. For bijels stabilized by rod like particles, the stress response of each processing 
condition is closer together, indicating a smaller variation in the response to the applied magnetic field compared to oblate particles. The shear response upon application
of the magnetic field also suggest that increased ordering of prolate particles makes the bijel more resistant to shear. I quantify the Herschel-Buckley fit parameters and 
tabulate the results in Table \ref{table:rheology_fit}.

@@

In Figure \ref{fig:particle_viz_tz}, the particles are initially ordered to the direction of the applied magnetic field. Upon application of shear and removal
of the magnetic field, I see that the particles begin reorienting away from the z direction. I also observe that the reorientation of particles uncovers the interface.
The reorientation observed is particle morphology specific with prolate particles seeing more reorientation away from the applied shear direction than oblate particles.
Looking at the images, I see that prolate particles rotate away from the direction of the magnetic field and applied shear towards the direction of the shear gradient,
while oblate particles reorient towards minimizing area to the applied shear direction. While these snapshots show the initial and final orientations of the particles at the
interface, the time evolution of the particle monolayer changes to identify its role in the rheological properties characterized.

@@

From Figure \ref{fig:interface_angle_shear}, I demonstrate that there is a slow increase in the interface angle over time for all cases
except for $\bar{B}: 0 \to 1$. For the $\bar{B}: 0 \to 1$ case, this has been shown in Chapter \ref{chapter:aim2} to be due to particle
reorientation to the applied magnetic field. For all other cases, we see an average increase in $\langle \psi \rangle$ over time, showing
that the particles under shear reorient out of the interface. Particles reorienting out of the interface can be due to shear induced interfacial 
stress, modifying the curvature of the interface and thus the lowest energy particle orientation to the interface or shear induced increases in
interparticle forces, causing the particle to tilt out of the interface to minimize interparticle forces. The latter 
mechanism can be characterized through measurements of the number of particles on the interface as increases in interparticle forces result in ejection of
particles from the interface.

@@

From the results in Figure \ref{fig:particles_interface_prop_shear}, the impact of the initial microstructure on the number of particles on the interface
differs for bijels stabilized by oblate and prolate ellipsoids. I split this analysis on processing history. While keeping the applied magnetic field
the same, little differences in the behavior of $n_{int}$ is observed, with small changes also being characterized for $\langle \psi \rangle$. 
Looking at the case of $\bar{B}:0 \rightarrow 0$, there is little change in the number of particles at the interface upon application of shear. This implies that the 
particles remain strongly adsorbed on the
interface. The $\langle \psi \rangle$ results also show this as this parameter increases slowly. This suggests that the particles remain firmly adsorbed
on the interface. Looking to the $\bar{B}:0 \rightarrow 1$ case, the number of particles at the interface drops while $\langle \psi \rangle$ increases. This
trend affects both particles which suggests that shear can pull particles out of the interface due to the decreased
interfacial adsorption energy the particle experiences when rotating out of the interface to orient to the applied field. The $\bar{B}:1 \rightarrow 1$ and 
$\bar{B}:1 \rightarrow 0$ have strong dependences on particle morphology. While an increase in $\langle \psi \rangle$ can be seen in both processing histories 
for both particle morphologies, a decrease in $n_{int}$ can be seen for prolate particles with processing history $\bar{B}:1 \rightarrow 0$ and for 
oblate particles with processing history $\bar{B}:1 \rightarrow 1$. We visualize $\langle \psi \rangle$ at the initial and final timestep for bijels stabilized with
oblate and prolate particles with processing $\bar{B}:1 \rightarrow 0$.
